Active Damping of Rotating Positioning Platforms

### 2020-06-23 paper/paper.tex
Update Figures, paper compiling fine

% Created 2020-06-22 lun. 17:38
% Intended LaTeX compiler: pdflatex
\documentclass{ISMA_USD2020}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{siunitx}
\usepackage{amsmath,amssymb,amsfonts, cases}
\usepackage{algorithmic, graphicx, textcomp}
\usepackage{xcolor, import, hyperref}
\usepackage[USenglish, english]{babel}
\setcounter{footnote}{1}
\input{config.tex}
\author[1,3] {T. Dehaeze}
\author[1,2] {C. Collette}
\affil[1] {Precision Mechatronics Laboratory\NewLineAffil University of Liege, Belgium \NewAffil}
\affil[2] {BEAMS Department\NewLineAffil Free University of Brussels, Belgium \NewAffil}
\affil[3] {European Synchrotron Radiation Facility \NewLineAffil Grenoble, France e-mail: \textbf{thomas.dehaeze@esrf.fr}}
\bibliographystyle{IEEEtran}
\date{}
\title{Active Damping of Rotating Positioning Platforms}
\begin{document}

@@

\section{Introduction}
\label{sec:org67e0a4e}
\label{sec:introduction}
\cite{dehaeze18_sampl_stabil_for_tomog_exper}

\section{System Under Study}
\label{sec:org85bcde2}
\subsection{Rotating Positioning Platform}
\label{sec:org4959a5e}
Consider the rotating X-Y stage of Figure \ref{fig:rotating_xy_platform}.

@@

\subsection{Equation of Motion}
\label{sec:orgdb109d9}
The system has two degrees of freedom and is thus fully described by the generalized coordinates \(u\) and \(v\).

@@

From the Lagrange's equations of the second kind \eqref{eq:lagrange_second_kind}, the equation of motion \eqref{eq:eom_mixed} is obtained (\(q_1 = u\), \(q_2 = v\)).
\begin{equation}
  \frac{d}{dt} \left( \frac{\partial L}{\partial \dot{q}_i} \right) + \frac{\partial D}{\partial \dot{q}_i} - \frac{\partial L}{\partial q_i} = Q_i
\end{equation}
with \(Q_i\) is the generalized force associated with the generalized variable \(q_i\) (\(Q_1 = F_u\) and \(Q_2 = F_v\)).

@@

\subsection{Transfer Functions in the Laplace domain}
\label{sec:orgfcd3def}

@@

\subsection{Constant Rotating Speed}
\label{sec:org81c7074}
To simplify, let's consider a constant rotating speed \(\dot{\theta} = \Omega\) and thus \(\ddot{\theta} = 0\).

@@

\section{Integral Force Feedback}
\label{sec:orgc6c1b99}
\subsection{Control Schematic}
\label{sec:orgb93b297}

@@

\subsection{Equations}
\label{sec:org4072ea4}
The sensed forces are equal to:
\begin{equation}
\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
\begin{bmatrix} F_u \\ F_v \end{bmatrix} - (c s + k)
\begin{bmatrix} d_u \\ d_v \end{bmatrix}
\end{equation}

@@

\subsection{Plant Dynamics}
\label{sec:org0250ac0}

@@

\subsection{Physical Interpretation}
\label{sec:orgb2d79d2}

@@

\section{Integral Force Feedback with High Pass Filters}
\label{sec:orgabf7a6a}
\subsection{Modification of the Control Low}
\label{sec:org4766bd6}

\subsection{Close Loop Analysis}
\label{sec:org4c639fd}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_modified_iff_bis.pdf}
\caption{\label{fig:root_locus_modified_iff}Figure caption}
\end{figure}

\subsection{Optimal Cut-Off Frequency}
\label{sec:orge829a45}

@@

\section{Integral Force Feedback with Parallel Springs}
\label{sec:orgd96ea25}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_iff_kp_bis.pdf}
\caption{\label{fig:root_locus_iff_kp_bis}Figure caption}
\end{figure}

@@

\section{Direct Velocity Feedback}
\label{sec:org027d051}

@@

\section{Comparison of the Proposed Active Damping Techniques}
\label{sec:org1eaa959}

@@

\section{Conclusion}
\label{sec:org1b2b4ae}
\label{sec:conclusion}

\section*{Acknowledgment}
\label{sec:org2ae16a5}

>>>>

% Created 2020-06-23 mar. 19:34
% Intended LaTeX compiler: pdflatex
\documentclass{ISMA_USD2020}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{siunitx}
\usepackage{amsmath,amssymb,amsfonts, cases}
\usepackage{algorithmic, graphicx, textcomp}
\usepackage{xcolor, import, hyperref}
\usepackage[USenglish, english]{babel}
\setcounter{footnote}{1}
\input{config.tex}
\author[1,3] {T. Dehaeze}
\author[1,2] {C. Collette}
\affil[1] {Precision Mechatronics Laboratory\NewLineAffil University of Liege, Belgium \NewAffil}
\affil[2] {BEAMS Department\NewLineAffil Free University of Brussels, Belgium \NewAffil}
\affil[3] {European Synchrotron Radiation Facility \NewLineAffil Grenoble, France e-mail: \textbf{thomas.dehaeze@esrf.fr}}
\bibliographystyle{IEEEtran}
\usepackage{tikz}
\usetikzlibrary{shapes.misc}
\date{}
\title{Active Damping of Rotating Positioning Platforms}
\hypersetup{
 pdfauthor={},
 pdftitle={Active Damping of Rotating Positioning Platforms},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.0.91 (Org mode 9.4)}, 
 pdflang={English}}
\begin{document}

@@

\section{Introduction}
\label{sec:org977317c}
\label{sec:introduction}
Controller Poles are shown by black crosses (
\begin{tikzpicture} \node[cross out, draw=black, minimum size=1ex, line width=2pt, inner sep=0pt, outer sep=0pt] at (0, 0){}; \end{tikzpicture}
).
\cite{dehaeze18_sampl_stabil_for_tomog_exper}

\section{System Under Study}
\label{sec:org042e800}
\subsection{Rotating Positioning Platform}
\label{sec:org489e4b9}
Consider the rotating X-Y stage of Figure \ref{fig:rotating_xy_platform}.

@@

\subsection{Equation of Motion}
\label{sec:orgb1836d5}
The system has two degrees of freedom and is thus fully described by the generalized coordinates \(u\) and \(v\).

@@

From the Lagrange's equations of the second kind, the equation of motion is obtained (\(q_1 = u\), \(q_2 = v\)).
\begin{equation}
  \frac{d}{dt} \left( \frac{\partial L}{\partial \dot{q}_i} \right) + \frac{\partial D}{\partial \dot{q}_i} - \frac{\partial L}{\partial q_i} = Q_i
\end{equation}
with \(Q_i\) is the generalized force associated with the generalized variable \(q_i\) (\(Q_1 = F_u\) and \(Q_2 = F_v\)).

@@

\subsection{Transfer Functions in the Laplace domain}
\label{sec:orgb1002ed}

@@

\subsection{Constant Rotating Speed}
\label{sec:orga4faf60}
To simplify, let's consider a constant rotating speed \(\dot{\theta} = \Omega\) and thus \(\ddot{\theta} = 0\).

@@

\section{Integral Force Feedback}
\label{sec:orgaf500b0}
\subsection{Control Schematic}
\label{sec:orgbd9f859}

@@

\subsection{Equations}
\label{sec:org48206d5}
The sensed forces are equal to:
\begin{equation}
\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
\begin{bmatrix} F_u \\ F_v \end{bmatrix} - (c s + k)
\begin{bmatrix} d_u \\ d_v \end{bmatrix}
\end{equation}

@@

\subsection{Plant Dynamics}
\label{sec:orgec8431d}

@@

\subsection{Physical Interpretation}
\label{sec:org159680e}

@@

\section{Integral Force Feedback with High Pass Filters}
\label{sec:org694707d}
\subsection{Modification of the Control Low}
\label{sec:org931fb10}

\subsection{Close Loop Analysis}
\label{sec:org9de0aa7}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_modified_iff_ter.pdf}
\caption{\label{fig:root_locus_modified_iff}Figure caption}
\end{figure}

\subsection{Optimal Cut-Off Frequency}
\label{sec:org9808de1}

@@

\section{Integral Force Feedback with Parallel Springs}
\label{sec:orgd4915d5}

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_iff_kp_ter.pdf}
\caption{\label{fig:root_locus_iff_kp_bis}Figure caption}
\end{figure}

@@

\section{Direct Velocity Feedback}
\label{sec:orgb0a5870}

@@

\section{Comparison of the Proposed Active Damping Techniques}
\label{sec:org6097c1d}

@@

\section{Conclusion}
\label{sec:org1624a6b}
\label{sec:conclusion}

\section*{Acknowledgment}
\label{sec:org1b29790}
